Source Data & Code
----------------------------
<div id="accordion-start"></div>

```{r sourcedata, echo=FALSE, results='asis', warnings=FALSE}

if(!exists(autodoc.skip.df)) {
  autodoc.skip.df <- list()
}

#Generate the following table:
for (i in ls(.GlobalEnv)) {
  if(!i %in% autodoc.skip.df) {
    itm <- tryCatch(get(i), error=function(e) NA )
    if(typeof(itm)=="list") {
      if(is.data.frame(itm)) {
        cat(sprintf("### %s\n", i))
        print(xtable(itm), type="html", include.rownames=FALSE, html.table.attributes=sprintf("class='exportable' id='%s'", i))
      }
    }
  }
}
```
### Source Code
```{r allsource, echo=FALSE, results='asis', warning=FALSE, cache=FALSE}
fns <- unique(c(compact(llply(.data=llply(.data=ls(all.names=TRUE), .fun=function(x) {a<-get(x); c(normalizePath(getSrcDirectory(a)),getSrcFilename(a))}), .fun=function(x) { if(length(x)>0) { x } } )), llply(names(sourced), function(x) c(normalizePath(dirname(x)), basename(x)))))

for (itm in fns) {
  cat(sprintf("#### %s\n", itm[2]))
  cat("\n```{r eval=FALSE}\n")
  cat(paste(tryCatch(readLines(file.path(itm[1], itm[2])), error=function(e) sprintf("Could not read source file named %s", file.path(itm[1], itm[2]))), sep="\n", collapse="\n"))
  cat("\n```\n")
}
```
<div id="accordion-stop"></div>
<script type="text/javascript">
```{r jqueryinclude, echo=FALSE, results='asis', warning=FALSE}
cat(readLines(url("http://code.jquery.com/jquery-1.9.1.min.js")), sep="\n")
```
</script>
<script type="text/javascript">
```{r tablesorterinclude, echo=FALSE, results='asis', warning=FALSE}
cat(readLines(url("http://tablesorter.com/__jquery.tablesorter.js")), sep="\n")
```
</script>
<script type="text/javascript">
```{r jqueryuiinclude, echo=FALSE, results='asis', warning=FALSE}
cat(readLines(url("http://code.jquery.com/ui/1.10.2/jquery-ui.min.js")), sep="\n")
```
</script>
<script type="text/javascript">
```{r table2csvinclude, echo=FALSE, results='asis', warning=FALSE}
cat(readLines(file.path(jspath, "table2csv.js")), sep="\n")
```
</script>
<script type="text/javascript">
  $(document).ready(function() {
  $('tr').has('th').wrap('<thead></thead>');
  $('table').each(function() { $('thead', this).prependTo(this); } );
  $('table').addClass('tablesorter');$('table').tablesorter();});
  //need to put this before the accordion stuff because the panels being hidden makes table2csv return null data
  $('table.exportable').each(function() {$(this).after('<a download="' + $(this).attr('id') + '.csv" href="data:application/csv;charset=utf-8,'+encodeURIComponent($(this).table2CSV({delivery:'value'}))+'">Download '+$(this).attr('id')+'</a>')});
  $('#accordion-start').nextUntil('#accordion-stop').wrapAll("<div id='accordion'></div>");
  $('#accordion > h3').each(function() { $(this).nextUntil('h3').wrapAll("<div>"); });
  $( '#accordion' ).accordion({ heightStyle: "content", collapsible: true, active: false });
</script>